\documentclass[11pt]{article}
\addtolength{\oddsidemargin}{-1.cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-2cm}
\addtolength{\textheight}{3.5cm}

\usepackage[pdftex]{graphicx}
\usepackage{pdflscape}
\usepackage{hyperref}
\usepackage{float}
\usepackage{cite}
\hypersetup{
	colorlinks=true,
	linkcolor=black,
	filecolor=magenta,
	urlcolor=cyan,
}

% define the title
\author{Team Longsword Notification}
\title{Phase 4 Testing Broadsword Notification}

\begin{document}
	\setlength{\parskip}{6pt}
	
	% generates the Cover page
	\input{CoverPage.tex}
	
	\tableofcontents
	
	\newpage
	
	
	\section{Create a list of service contracts tested}
	\subsection{Pre-conditions}
	\begin{itemize}
		\item User details such as email address do exist and are valid.
		\item Notification request is complete with details of the email for example the subject and body of the email.
		\item The user receiving the email exists in the system
	\end{itemize}
	\subsubsection{Post-conditions}
	\begin{itemize}
		\item At least one notification has been sent to the appropriate user/users.
		\item System should log who Notifications are sent to, if the Notification request is not successful, the error message should be logged as well.
	\end{itemize}
	\textbf{The Notifications services should only fail under Three conditios that are:}
	\begin{itemize}
		\item Request has failed to meet the validation criteria specified in the post conditions.
		\item The request information is incomplete or has an error.
		\item There actually is no notification for the user.
	\end{itemize}
	\subsection{Team Broadsword Notification Serices}
	For this section we inspected the code of the Team Broadsword email services.
	\section{Create a list of non-functional requirements tested}
	\section{Evaluate the test cases of the previous team for non-functional requirements using your own criteria}	
	\section{Add more tests if required}


	
	
\end{document}
